TITLE

### 2021-02-26 outputs/Paper.Rmd
update graphs

library(tidyverse)
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
library(ggplot2)
library(kableExtra)

@@

The first six rows of raw data is shown in the Table1. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
#plot row data set in table
  head(simulated_data)%>%
  select(-size)%>%
  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
### T-Test
```{r ttest,echo=FALSE}
#install.packages("broom")
library(broom)
revenue_c <- control_data$Q13
revenue_t <- treated_data$Q13
t<-t.test(revenue_t, revenue_c)
m<-tidy(t, digits=1)
m%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    mean_of_Treated=estimate1,
    mean_of_Control=estimate2
  )%>%
  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()

### Revenue distributions group by restaurant size
```{r revenue_distribution, echo=FALSE}
library(ggplot2)
library(ggthemes)
# Treated group
rd1<-
  ggplot(treated_data, aes(x = treated_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# Control group
rd2<-
  ggplot(control_data, aes(x = control_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# combine two diagram in one graph
#install.packages("ggpubr")
library(ggpubr)
ggarrange(
  rd1, rd2, 
  ncol = 1, nrow = 2,
  heights = c(1, 1),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )
```

### restaurant type by regions

@@

library(viridis)

@@

### Flex and fiexed cost changes

```{r felx_fix, echo=FALSE, fig.width=10, fig.height=4}

# Treated group

# Fixed costs 
fixc1<-
  ggplot(treated_data, aes(fill= Q11, x=Q11)) +
  geom_bar(stat="count", width = 0.5)+
    ggtitle("Fixed costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# flex cost
flexc1<-
    ggplot(treated_data, aes(fill= Q12, x=Q12)) +
    geom_bar(stat="count", width = 0.5)+
    ggtitle("Treated Group: Flexible costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# Control group
fixc2<-
  ggplot(control_data, aes(fill= Q11, x=Q11)) +
  geom_bar(stat="count", width = 0.5)+
    ggtitle("Fixed costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

fixc2<- fixc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# flex cost
flexc2<-
    ggplot(control_data, aes(fill= Q12, x=Q12)) +
    geom_bar(stat="count", width = 0.5)+
    ggtitle("Control Group: Flexible costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

flexc2<- flexc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# combine two diagram in one graph
ggarrange(
  flexc1,fixc1,flexc2, fixc2,
  ncol = 2, nrow = 2,
  vjust = 1,
  widths = c(2, 2),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

### Distribution average employee salary
```{r salary_distribution, echo=FALSE, fig.width=10, fig.height=4}
library(ggthemes)
# Treated group
s1<-
  ggplot(treated_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Salary Distributions in Treated Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ # add dots
  theme_economist()

# Control group
s2<-
  ggplot(control_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Salary Distributions in Control Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ #add dots
  theme_economist()

@@

### correlation matrix
```{r correlation, echo=FALSE, fig.width=20, fig.height=20}
#install.packages("fastDummies")
library(fastDummies)
Dummy_data<-simulated_data[-c(1,2,10)]

Dummy_data<- fastDummies::dummy_cols(Dummy_data)

# correlation matrix for Big restaurants
Dummy_data<-Dummy_data[-c(1:3,5:10,12,43)]

# Compute a correlation matrix
corr <- round(cor(Dummy_data), 1)

@@

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot1 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )
corr.plot1

# correlation matrix for Small restaurants
Dummy_data<-simulated_data[-c(1,2,10)]
Dummy_data<- fastDummies::dummy_cols(Dummy_data)
Dummy_data<-Dummy_data[-c(1:3,5:10,12,42)]

# Compute a correlation matrix
corr <- round(cor(Dummy_data), 1)

# Compute a matrix of correlation p-values
library(ggcorrplot)
p.mat <- cor_pmat(Dummy_data)

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot2 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )
corr.plot2

ggarrange(
  corr.plot1, corr.plot2, 
  labels = c('Big restaurant', 'Small restaurant'),
  ncol = 2, nrow = 1,
  align = "hv"
  )

>>>>

library(tidyverse)
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
library(ggplot2)
library(kableExtra)
library(ggpubr)
```

@@

The first six rows of raw data is shown in the Table1. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
#plot row data set in table
  head(simulated_data)%>%
  select(-size)%>%
  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()
```
### EDA

```{r restaurant_number, echo=FALSE, fig.width=6, fig.height=5}
R1<-simulated_data%>%
  ggplot(aes(x = simulated_data$Q2,fill = type)) +
  geom_bar(stat = "count", position = "dodge") +
  labs(title = "More restuarants are loacted in City of Toronto and Peel Region",x="Regions") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

R2<-simulated_data%>%
  ggplot(aes(x = simulated_data$Q3 ,fill = type)) +
  geom_bar(stat = "count", position = "dodge") +
  labs(title = "More restuarants in GTA are casual dinning ",x="Regions") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

# combine two diagram in one graph
ggarrange(
  R1,R2,
  ncol = 1, nrow = 2,
  vjust = 1,
  widths = c(2, 2),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )
```

@@

library(viridisLite)

@@

```{r salary_distribution, echo=FALSE, fig.width=10, fig.height=4}
library(ggthemes)
# Treated group
s1<-
  ggplot(treated_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Salary Distributions in Treated Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01, binwidth =1)+ # add dots
  theme_economist()

# Control group
s2<-
  ggplot(control_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4)+
  labs(title="Salary Distributions in Control Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01,binwidth =1)+ #add dots
  theme_economist()

@@

```{r franchise, echo=FALSE, fig.width=10, fig.height=4}

Pie1<-control_data%>%
  ggplot(aes(x = control_data$Q4 ,fill = Q4)) +
  geom_bar(stat = "count", position = "dodge") +
  coord_polar("y", start=0)+   #Create a pie chart based on the barplot
  labs(title = "Franchise restaurants slightly decrease in treated group ",x="Regions",y="Count in control group") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

Pie2<-treated_data%>%
  ggplot(aes(x = treated_data$Q4 ,fill = Q4)) +
  geom_bar(stat = "count", position = "dodge") +
  coord_polar("y", start=0)+
  labs(title = "",x="Regions", y="Count in treated group") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

#Merge twp graphs
ggarrange(
  Pie1, Pie2, 
  ncol = 2, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )
```

```{r employee#, echo=FALSE, fig.width=10, fig.height=4}
cxc <- 
  simulated_data%>%
  ggplot(aes(x = simulated_data$Q8 ,fill = type)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
  scale_fill_manual(values = c("Red", "Blue"))+
  labs(title = "Almost 0 restaurant has more than 30 employees in control group",x="", y="Count") +
  theme_minimal()

cxc
```

### T-Test
```{r ttest,echo=FALSE}
#install.packages("broom")
library(broom)
revenue_c <- control_data$Q13
revenue_t <- treated_data$Q13
t<-t.test(revenue_t, revenue_c)
m<-tidy(t, digits=1)
m%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    mean_of_Treated=estimate1,
    mean_of_Control=estimate2
  )%>%
  kableExtra::kbl(caption = "T Test on the Restaurant's revenue") %>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kable_styling()

### Invention effect on Revenue distributions

```{r revenue_distribution, fig.cap="Revenue distribution",echo=FALSE}

library(ggthemes)
# Treated group
rd1<-
  ggplot(simulated_data, aes(x = simulated_data$Q13/1000, fill=type)) +
  geom_histogram(position = "dodge", bins = 30,binwidth = 5) +
  scale_fill_manual(values = c("red", "blue"))+
  labs(title="Revenue Distributions Move to the right", x="Renvenue (Thousands)", y="Count")+
  geom_density()+
  theme_calc()

rd1

```
Two merged histograms charts were used to illustrate the restaurant's revenue distribution.

(Figure \@ref(fig:revenue_distribution))

### Invention effect on Flex and fiexed cost

```{r felx_fix, echo=FALSE, fig.width=6, fig.height=4}
# Treated group

# Fixed costs 
fixc1<-
  ggplot(simulated_data, aes(fill= type, x=Q11)) +
  geom_bar(stat="count", width = 0.6,position = "dodge")+
  scale_fill_manual(values = c("red", "blue"))+
    ggtitle("Fixed costs increased in treated group and remain same in control group") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()
fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# flex cost
flexc1<-
    ggplot(simulated_data, aes(fill= type, x=Q12)) +
    geom_bar(stat="count", width = 0.7, position = "dodge")+
    scale_fill_manual(values = c("red", "blue"))+
    ggtitle("Flexible costs increased in most of treated group restaurants") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()
flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# combine two diagram in one graph
ggarrange(
  flexc1,fixc1,
  ncol = 1, nrow = 2,
  vjust = 1,
  widths = c(2, 2),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

### correlation matrix
```{r correlation, echo=FALSE, fig.width=20, fig.height=10}
#install.packages("fastDummies")
library(fastDummies)
Dummy_data<-treated_data[-c(1,2)] #Remove Type and postcode columns

Dummy_data<- fastDummies::dummy_cols(Dummy_data) #  change categorical var to factors

# correlation matrix for restaurants in treated group
Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)] # remove big restaurant, cause it will always has -1 relationship with small restaurant

# Compute a correlation matrix
corr <- round(cor(Dummy_data), 1) # round to 1 digit

@@

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot1 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )

# correlation matrix for restaurants in control group
Dummy_data<-control_data[-c(1,2)] #Remove Type and postcode columns

Dummy_data<- fastDummies::dummy_cols(Dummy_data) #  change categorical var to factors

Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)]

# Compute a correlation matrix
corr <- round(cor(Dummy_data), 1) # round to 1 digit

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot2 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )
# combine two diagram in one graph

ggarrange(
  corr.plot1, corr.plot2, 
  labels = c('Treated group', 'Control group'),
  ncol = 2, nrow = 1,
  align = "hv"
  )
